SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-17 paper/experiments.tex
related-work

In table~\ref{tbl:qf-results} 
\b PARTIAL ...

\begin{table}[!ht]
\centering
\def\arraystretch{1.6}
\caption{
{\bf Activity regulation of molecules and corresponding connectivity of the graph.}}
  \begin{tabular}{|c|l|l|c|c|}
    \hline
  \multirow{2}{*}{\textbf{Sr.No}}  & \multicolumn{2}{c|}{\textbf{Activity mechanism}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-5}
    {} & \multirow{1}{*} {\bf{ On compartment}} & \multirow{1}{*} {\bf{On vesicle}}  & \textbf{\textbf{Least}} & \textbf{Highest}\\
    %\hhline{~--}
    \hline
E. & Boolean function & Boolean function & 2-connected & 3-connected \\ \hline
C. & None & Boolean function & 3-connected & 3-connected \\  \hline
F. & Boolean function & Pairing inhibition & 4-connected & 4-connected \\ \hline
D. & None & Pairing inhibition & No graph & No graph \\ \hline
B. & Boolean function & None & No graph & No graph \\ \hline
A. & None & None & No graph & No graph \\ \hline
G. & Boolean function & Every edge is distict & 3-connected & 3-connected \\ \hline
H. & Self edges are allowed & Boolean funcion & No-idea & No-idea \\ \hline

>>>>

In table~\ref{tbl:qf-results} 
\b PARTIAL .... Form change is proposed in the table and table will consists of constraints used in the model rather than the model itself.

\begin{table}[!ht]
\centering
\def\arraystretch{1.6}
\caption{
{\bf Activity regulation of molecules and corresponding connectivity of the graph.}}
  \begin{tabular}{|c|l|l|c|c|}
    \hline
  \multirow{2}{*}{\textbf{Sr.No}}  & \multicolumn{2}{c|}{\textbf{Activity mechanism}} &  \multicolumn{2}{c|}{\textbf{Graph connectivity}}  \\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-5}
    {} & \multirow{1}{*} {\bf{ On compartment}} & \multirow{1}{*} {\bf{On vesicle}}  & \textbf{\textbf{Least}} & \textbf{Highest}\\
    %\hhline{~--}
    \hline
E. & Boolean function & Boolean function & 2-connected & 3-connected \\ \hline
C. & None & Boolean function & 3-connected & 3-connected \\  \hline
F. & Boolean function & Pairing inhibition & 4-connected & 4-connected \\ \hline
D. & None & Pairing inhibition & No graph & No graph \\ \hline
B. & Boolean function & None & No graph & No graph \\ \hline
A. & None & None & No graph & No graph \\ \hline
G. & Boolean function & Every edge is distinct & 3-connected & 3-connected \\ \hline
H. & Self edges are allowed & Boolean function & No-idea & No-idea \\ \hline
